Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-11 paper.tex
Suite intro

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}

@@

	Let $(\gamma^{k_l})$ be a subsequence of $(\gamma^l)$ that converges to $\zeta$.
	Let us denote, for convenience, $T_1 = P_{\Ccal_2}^\theta \circ P_{\Ccal_1}^\theta$ and $T_2 = P_{\Ccal_2} \circ P_{\Ccal_1}$ the two operators used in the iteration, and $T$ the compound operator, so that $T_{|U} \equiv T_{1|U}$ and $T_{|U^c} \equiv T_{2|U^c}$.
	\begin{itemize}
		\item If $\zeta \in U$, then since $U$ is open, all $(\gamma^{k_l})$ are eventually in $U$ as well.
		Thus, for any large enough $l$, $ T(\gamma^{k_l}) = T_1(\gamma^{k_l}) $. By continuity of $T_1$ on $U$, since $(\gamma^{k_l})$ converges to $\zeta$, 
		\[T(\zeta) = \lim_{l\rightarrow \infty} T(\gamma^{k_l}).\] Thus
		 \[F(T(\zeta)) = \lim_{l \rightarrow \infty} F(T(\gamma^{k_l})) \ge \lim_{l\rightarrow \infty} F(\gamma^{k_{l+1}}) .\]
		 \[
		 F(T(\zeta)) \ge F(\zeta)
		 \] Since $\zeta$ is inside the set $U$, which ensures strict decrease of the Lyapunov function, this is absurd.
		 \item If $\zeta \in U^c$ and an infinite number of $(\gamma^{k_l})$ are in $U^c$, then the same argument of continuity applied to $T_2$ yields
		 \[
		 F(T(\zeta)) = F(\zeta).
		 \]
		 The function $\varphi_1$ from lemma \ref{lemma:lyapunov_decrease} is strictly positive except at $x=1$. Since the case of equality occurs for both projections, this ensures that $\zeta \in \Ccal_1 \cap \Ccal_2$.

		 \item If $\zeta \in U^c$ and all but finitely many $\gamma^{k_l}$ are in $U$, then $\zeta$ is on the border $\partial U$. In particular it belongs to $\bar{U}$, and therefore
		 \[
		 F(P^\omega_{\Ccal_1}(\zeta)) \le F(\zeta) \quad
		 \text{ and } \quad
		 F(P^\omega_{\Ccal_2}(P^\theta_{\Ccal_1}(\zeta))) \le F(P^\theta_{\Ccal_1}(\zeta)).
		 \]
		 By lemma \ref{lemma:F_P_theta}, the inequality \begin{equation} \label{eq:ineq1}
		 F(P_{\Ccal_1}^\theta(\zeta)) \le F(P_{\Ccal_1}^\omega(\zeta)) \end{equation}
		 is valid; it is strict unless $\zeta \in \Ccal_1$.
		 The same lemma yields
		 \begin{equation} \label{eq:ineq2}
		 F(P_{\Ccal_2}^\theta(P_{\Ccal_1}^\theta(\zeta)) \le F(P_{\Ccal_2}^\omega(P_{\Ccal_1}^\theta(\zeta)), \end{equation}
		 with a strict inequality unless $P_{\Ccal_1}^\theta(\zeta) \in \Ccal_2$.
		 To sum up, we have the series of inequalities:
		 \[
		 F(\zeta) 
		 \overset{\zeta \in \bar{U}}{\ge}
		 F(P^\omega_{\Ccal_1}(\zeta))
		 \overset{\text{(\ref{eq:ineq1})}}{\ge}
		 F(P^\theta_{\Ccal_1}(\zeta))
		 \overset{\zeta \in U}{\ge}
		 F(P_{\Ccal_2}^\omega(P_{\Ccal_1}^\theta(\zeta)))
		 \overset{\text{(\ref{eq:ineq2})}}{\ge}
		 F(P_{\Ccal_2}^\theta(P_{\Ccal_1}^\theta(\zeta)))
		 \]

		 Yet, by continuity of $T_1 = P_{\Ccal_2}^\theta \circ P_{\Ccal_1}^\theta $ on $\bar{U}$, we have
		 \[
		 F(P_{\Ccal_2}^\theta(P_{\Ccal_1}^\theta(\zeta))) = F(\zeta).
		 \]
		 Thus both (\ref{eq:ineq1}) and (\ref{eq:ineq2}) fall in the case of equality, which means $\zeta \in \Ccal_1$ and $P^\theta_{\Ccal_1}(\zeta) = \zeta \in \Ccal_2$.
	\end{itemize}
\end{proof}

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools,enumitem}

@@

	Let $(\gamma^{k_l})$ be a subsequence of $(\gamma^l)$ that converges to $\zeta$.
	Let us denote, for convenience, $T_1 = P_{\Ccal_2}^\theta \circ P_{\Ccal_1}^\theta$ and $T_2 = P_{\Ccal_2} \circ P_{\Ccal_1}$ the two operators used in the iteration, and $T$ the compound operator, so that $T_{|U} \equiv T_{1|U}$ and $T_{|U^c} \equiv T_{2|U^c}$.
	\begin{enumerate}[align=right,labelsep=10pt,leftmargin=0.5cm]
		\item[$\bullet$] If $\zeta \in U$, then since $U$ is open, all $(\gamma^{k_l})$ are eventually in $U$ as well.
		Thus, for any large enough $l$, $ T(\gamma^{k_l}) = T_1(\gamma^{k_l}) $. By continuity of $T_1$ on $U$, since $(\gamma^{k_l})$ converges to $\zeta$, 
		\[T(\zeta) = \lim_{l\rightarrow \infty} T(\gamma^{k_l}).\] Thus
		 \[F(T(\zeta)) = \lim_{l \rightarrow \infty} F(T(\gamma^{k_l})) \ge \lim_{l\rightarrow \infty} F(\gamma^{k_{l+1}}) .\]
		 \[
		 F(T(\zeta)) \ge F(\zeta)
		 \] Since $\zeta$ is inside the set $U$, which ensures strict decrease of the Lyapunov function, this is absurd.
		\item[$\bullet$] If $\zeta \in U^c$ and an infinite number of $(\gamma^{k_l})$ are in $U^c$, then the same argument of continuity applied to $T_2$ yields
		 \[
		 F(T(\zeta)) = F(\zeta).
		 \]
		 The function $\varphi_1$ from lemma \ref{lemma:lyapunov_decrease} is strictly positive except at $x=1$. Since the case of equality occurs for both projections, this ensures that $\zeta \in \Ccal_1 \cap \Ccal_2$.

		 \item[$\bullet$] If $\zeta \in U^c$ and all but finitely many $\gamma^{k_l}$ are in $U$, then $\zeta$ is on the border $\partial U$. In particular it belongs to $\bar{U}$, and therefore
		 \[
		 F(P^\omega_{\Ccal_1}(\zeta)) \le F(\zeta) \quad
		 \text{ and } \quad
		 F(P^\omega_{\Ccal_2}(P^\theta_{\Ccal_1}(\zeta))) \le F(P^\theta_{\Ccal_1}(\zeta)).
		 \]
		 By lemma \ref{lemma:F_P_theta}, the inequality \begin{equation} \label{eq:ineq1}
		 F(P_{\Ccal_1}^\theta(\zeta)) \le F(P_{\Ccal_1}^\omega(\zeta)) \end{equation}
		 is valid; it is strict unless $\zeta \in \Ccal_1$.
		 The same lemma yields
		 \begin{equation} \label{eq:ineq2}
		 F(P_{\Ccal_2}^\theta(P_{\Ccal_1}^\theta(\zeta)) \le F(P_{\Ccal_2}^\omega(P_{\Ccal_1}^\theta(\zeta)), \end{equation}
		 with a strict inequality unless $P_{\Ccal_1}^\theta(\zeta) \in \Ccal_2$.
		 To sum up, we have the series of inequalities:
		 \[
		 F(\zeta) 
		 \overset{\zeta \in \bar{U}}{\ge}
		 F(P^\omega_{\Ccal_1}(\zeta))
		 \overset{\text{(\ref{eq:ineq1})}}{\ge}
		 F(P^\theta_{\Ccal_1}(\zeta))
		 \overset{\zeta \in U}{\ge}
		 F(P_{\Ccal_2}^\omega(P_{\Ccal_1}^\theta(\zeta)))
		 \overset{\text{(\ref{eq:ineq2})}}{\ge}
		 F(P_{\Ccal_2}^\theta(P_{\Ccal_1}^\theta(\zeta)))
		 \]

		 Yet, by continuity of $T_1 = P_{\Ccal_2}^\theta \circ P_{\Ccal_1}^\theta $ on $\bar{U}$, we have
		 \[
		 F(P_{\Ccal_2}^\theta(P_{\Ccal_1}^\theta(\zeta))) = F(\zeta).
		 \]
		 Thus both (\ref{eq:ineq1}) and (\ref{eq:ineq2}) fall in the case of equality, which means $\zeta \in \Ccal_1$ and $P^\theta_{\Ccal_1}(\zeta) = \zeta \in \Ccal_2$.
	\end{enumerate}
\end{proof}
